\section{Methods}
\label{sec:methods}

% = PARAGRAPH 1 - Overview of the evaluation pipeline


\subsection{Evaluation pipeline}

We reuse the existing \code{automatic\_eval.py} pipeline from the COMET-ATOMIC-2020 repository\footnote{Our modified code is available at: \url{https:github.com/Harmxn02/KTAI-Project-comet-atomic-2020}}, without any model retraining. The input consists of the pregenerated BART output file (\code{BART-atomic\_2020.json}), which contains greedy-decoded tails for the ATOMIC2020 test set, paired against reference tails from \code{test.tsv}. This setup has a twofold purpose: it allows us to verify the results from the original paper, and it allows us to make small modifications to the evaluation pipeline to support our proposed partitioning strategy.


% = PARAGRAPH 2 - Partitioning strategy

\subsection{Partitioning strategy}

Each test example was assigned a category based on its relation type, using the three-way taxonomy from Table 7 of \citet{hwang2021cometatomic}: social-interaction, physical-entity, and event-centred. Scores were accumulated both at the individual relation level (23 types) and aggregated up to the category level. This partitioning strategy was chosen over alternatives like query length or output length because the three different category types represent different types of general knowledge and should also be evaluated as a group rather than as 23 separate relations.


% = PARAGRAPH 3 - Object function / scoring

\subsection{Scoring}

We use BLEU-1 through BLEU-4 as the evaluation metrics, reporting all four variants to provide a more comprehensive picture of n-gram overlap between generated and reference tails. In comparison, Table 3 in \citet{hwang2021cometatomic} only reports BLEU-1 scores. Following the convention in the original code, \code{none} responses are excluded from scoring, so that only valid generations are evaluated.

% = PARAGRAPH 4 - Variations considered

\subsection{Alternative partitioning strategies}

Whereas the original paper benchmarked at a fine-grained per-relation level, we report both per-relation (fine-grained, 23 groups) and per-category (coarse-grained, 3 groups) scores as variations of the same method.  We also considered alternative partitioning strategies based on query length or output length, but opted for relation type because it maps directly onto the knowledge graph structure. It is also most directly comparable to the paper's own per-relation human evaluation.
